\section{Foundations and Motivation}

\subsection{From ``Fail-Stop'' to ``Byzantine Fault''}
In the 1980s, fault tolerance research was heavily concentrated on \textit{fail-stop} faults, which occur when a node simply ceases to operate, typically due to a hardware crash. However, as systems grew more complex, these failures became just the tip of the iceberg. 

A node can fail due to software bugs or be compromised by malicious attackers. In these scenarios, the defective node does not shut down; it continues to communicate but can behave arbitrarily or transmit false information. This arbitrary behavior is known as a \textbf{Byzantine Fault}. Within a Byzantine environment, it is assumed that defective nodes actively conspire to corrupt the system state.

\subsection{The pBFT System Model}
The pBFT algorithm assumes a realistic and hostile system model:
\begin{itemize}
    \item \textbf{Asynchrony:} It operates in an asynchronous distributed system, such as the Internet, where messages can be delayed, lost, or delivered out of order.
    \item \textbf{Strong Adversary:} It posits an adversary capable of coordinating compromised nodes. pBFT relies heavily on cryptography (public-key signatures, MACs, cryptographic digests) to secure message integrity.
    \item \textbf{Safety without Synchrony:} It guarantees its safety property (contradictory operations will never be committed) regardless of network delays, relying only on weak synchrony for liveness.
\end{itemize}
\begin{tikzpicture}[
        font=\sffamily,
        node distance=0.8cm and 0.4cm,
        % Core Style
        core/.style={rectangle, draw=black, line width=1.2pt, inner sep=10pt, align=center, font=\sffamily\bfseries, text width=6cm},
        % Pillar Style
        pillar/.style={rectangle, draw=gray!80, line width=0.8pt, inner sep=6pt, align=center, font=\sffamily\bfseries, text width=4cm, minimum height=1cm},
        % Detail Style
        detail/.style={rectangle, draw=gray!20, fill=gray!2, rounded corners=2pt, align=left, inner sep=6pt, text width=4cm, font=\sffamily\scriptsize},
        % Arrow Styles
        link/.style={-{Stealth[length=2mm]}, draw=gray!60, line width=0.6pt},
        interrelation/.style={Stealth-Stealth, draw=black!80, line width=0.6pt, dashed}
    ]

        % Central Core (Top)
        \node[core] (core) {
            pBFT System Model\\
            \mdseries\small``Never trust, always verify''\\
            \mdseries\footnotesize(Zero Trust Architecture)
        };

        % Three Pillars (Middle Row)
        \node[pillar, below=1.2cm of core] (p2) {
            2. Strong Adversary\\
            \mdseries\small[The Threat]
        };

        \node[pillar, left=of p2] (p1) {
            1. Asynchrony\\
            \mdseries\small[The Environment]
        };

        \node[pillar, right=of p2] (p3) {
            3. Safety vs Synchrony\\
            \mdseries\small[The Guarantee]
        };

        % Connect Core to Pillars
        \draw[link] (core) -- (p1.north);
        \draw[link] (core) -- (p2.north);
        \draw[link] (core) -- (p3.north);

        % Details (Bottom Row)
        \node[detail, below=0.4cm of p1] (d1) {
            $\bullet$ Unpredictable network\\
            $\bullet$ Arbitrary message delays\\
            $\bullet$ Dropped or reordered data\\
            $\bullet$ Internet-scale chaos
        };
        \draw[link] (p1) -- (d1);

        \node[detail, below=0.4cm of p2] (d2) {
            $\bullet$ Active, coordinated attacks\\
            $\bullet$ Hackers \& faulty nodes\\
            $\bullet$ \textbf{Mitigation:} Cryptography\\
            \hspace*{2mm}(Signatures, MACs, Hashes)
        };
        \draw[link] (p2) -- (d2);

        \node[detail, below=0.4cm of p3] (d3) {
            $\bullet$ \textbf{Safety:} Absolute data integrity; zero corruption.\\
            $\bullet$ \textbf{Liveness:} Weak synchrony needed (pauses instead of erring).
        };
        \draw[link] (p3) -- (d3);

        % Interrelation Arc between P1 and P3
        \draw[interrelation] (p1.north east) to[bend left=12] 
            node[above, font=\sffamily\tiny\itshape, text width=5cm, align=center, yshift=1mm] {
                Defines network chaos $\longleftrightarrow$ Guarantees integrity despite chaos
            } 
            (p3.north west);

    \end{tikzpicture}

\subsection{The $3f+1$ Rule}
To tolerate $f$ Byzantine failures, the minimum number of replicas required is $n = 3f+1$. This is because the protocol must be able to make progress using responses from $n - f$ replicas (since $f$ nodes could be dead or unresponsive). Within those received responses, $f$ nodes could be malicious liars. For the honest nodes' votes to strictly outvote the malicious ones, the following inequality must hold: $(n - f) - f > f \implies n > 3f$.

Another perspective to understand this rule is through quorum intersections. Committing an operation requires a quorum of $2f+1$ identical responses. If two distinct quorums of $2f+1$ intersect, their mathematical overlap will always contain at least $f+1$ replicas, inherently guaranteeing at least one honest node in the intersection.

\begin{figure}[H]
\centering
\begin{tikzpicture}[scale=1.5, every node/.style={transform shape}]
    \draw[fill=blue!40, opacity=0.6, draw=black, thick] (0,0) circle (1.5);
    \draw[fill=red!40, opacity=0.6, draw=black, thick] (1.5,0) circle (1.5);
    \node[text=black, font=\bfseries] at (-0.5,0) {$Q_1$};
    \node[text=black, font=\bfseries] at (2.0,0) {$Q_2$};
    \node[text=black, font=\bfseries] at (0.75,0) {$\ge f+1$};
\end{tikzpicture}
\caption{Quorum Intersection in pBFT}
\end{figure}